Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex
use cref
use cleveref for referencing section, caption and tables #25

This paper is organized as follows: Section~\ref{sec:kub-workflow} discusses KUB's current workflow, Section~\ref{sec:urban-building} provides an overview of some modeling and simulation components, and finally, Section~\ref{sec:cicd-framework} delves into the CI/CD processes from standard DevOps to HPCops tailored for EuroHPC environments.

@@

The Ktirio urban building workflow, see Figure~\ref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments. The process encompasses data acquisition, processing, simulation, and analysis, eventually coupled with Urban Air Pollution (UAP) models.

@@

This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation). Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh. The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling). \textit{(iii)} Apply the intersection of vegetation with buildings and terrain; and finally \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).

@@

The figure~\ref{fig:partitioning} illustrates the different strategies discussed previously and presents a reconstruction of New York City in figure \ref{fig:city-ny-largescale}. This geometric model has an area of 400 $km^2$ (20 km square side of 20 km) and has generated around 450000 buildings. This example requires the large-scale approach discussed but not yet implemented or tested.

@@

In the figure~\ref{fig:solar-masks-vf}, we illustrate \textit{(i)} the solar masks of building face oriented eastwise for a discretization of the sun position in the panel~\ref{fig:sm-building-east}, \textit{(ii)} the solar masks for an entire building for discretization of the sun position in the panel~\ref{fig:sm-whole-building}, \textit{(iii)} a visualization of the solar mask early morning of the city center of Strasbourg in panel~\ref{fig:sm-strasbourg} and \textit{(iv)} an image of a standard benchmark~\cite{van_eck_surface_2016} for the computation of view-factors and solving the heat transfer problems between three building blocks in 2D subsequently in panel~\ref{fig:view-factor}.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-feelpp-devops.pdf}
    \caption{CI/CD DevOps for Feel++}
    \label{fig:feelpp-devops}
\end{figure}
The CI/CD workflow, see Figure~\ref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. The workflow leverages various main ingredients of GitHub Actions features.
\begin{enumerate}
    \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
    \item \textbf{Graphical User Interface (GUI) thanks to \texttt{workflow\_dispatch}:} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing.
    \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
\end{enumerate}

@@

Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++.
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-feelpp-hpcops.pdf}
    \caption{CI/CD HPCOps for Feel++}
    \label{fig:feelpp-hpcops}
\end{figure}

@@

Figure~\ref{fig:kub-devops} shows that the CI/CD standard DevOps framework for KUB uses similar steps.

Figure~\ref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot on large-scale cases. It extends Feel++ HPC ops with additional steps to handle our complex pre- and post-processing steps.

@@

Finally, we display some results of our benchmarking activities~\cite{hidalgo2_d31_2024} for the KUB application regarding HPC performance.
Running these experiments regularly is essential for maintaining the program's efficiency when developing the application and after machine updates.
Hence, we have used the KUB application in the Strasbourg city center, with a square area of $4 \mathrm{km}^2$ (approximately 17K buildings).
The scalability results were realized on EuroHPC JU systems obtained with our HPCOps pipeline; see Figure~\ref{fig:kub-hpcops}.
Figure \ref{fig:scalability} depicts the speedup achieved on Discoverer, Karolina, and MeluXina.
They present results for the total execution (end-to-end) of the KUB application and the simulation component.

@@

To better understand what causes this degradation, we measure the computing times of the different stages of the pipeline and present the execution breakdown in Figure \ref{fig:execution-breakdown}. This figure reports the portion of the total execution taken by:
\begin{itemize}
\item Pre-processing (Pre-proc): The time elapsed in initialization before entering the time loop of the simulation
\item Simulation (Simulation): The cumulative time spent calculating the new solution at each time step
\item Post-processing (Post-proc): The cumulative time spent exporting results, i.e., generating files containing the output of the UB model.
\end{itemize}

>>>>

This paper is organized as follows: \cref{sec:kub-workflow} discusses KUB's current workflow, \cref{sec:urban-building} provides an overview of some modeling and simulation components, and finally, \cref{sec:cicd-framework} delves into the CI/CD processes from standard DevOps to HPCops tailored for EuroHPC environments.

@@

The Ktirio urban building workflow, see \cref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments. The process encompasses data acquisition, processing, simulation, and analysis, eventually coupled with Urban Air Pollution (UAP) models.

@@

This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation). Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh. 
\Cref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling). \textit{(iii)} Apply the intersection of vegetation with buildings and terrain; and finally \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).

@@

\Cref{fig:partitioning} illustrates the different strategies discussed previously and presents a reconstruction of New York City in \cref{fig:city-ny-largescale}. This geometric model has an area of 400 $km^2$ (20 km square side of 20 km) and has generated around 450000 buildings. This example requires the large-scale approach discussed but not yet implemented or tested.

@@

In \cref{fig:solar-masks-vf}, we illustrate \textit{(i)} the solar masks of building face oriented eastwise for a discretization of the sun position in \cref{fig:sm-building-east}, \textit{(ii)} the solar masks for an entire building for discretization of the sun position in \cref{fig:sm-whole-building}, \textit{(iii)} a visualization of the solar mask early morning of the city center of Strasbourg in \cref{fig:sm-strasbourg} and \textit{(iv)} an image of a standard benchmark~\cite{van_eck_surface_2016} for the computation of view-factors and solving the heat transfer problems between three building blocks in 2D subsequently in \cref{fig:view-factor}.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-feelpp-devops.pdf}
    \caption{CI/CD DevOps for Feel++}
    \label{fig:feelpp-devops}
\end{figure}
The CI/CD workflow, see \cref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. 
The workflow leverages various main ingredients of GitHub Actions features.
\begin{enumerate}
    \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
    \item \textbf{Graphical User Interface (GUI) thanks to \texttt{workflow\_dispatch}:} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing.
    \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
\end{enumerate}

@@

\Cref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++.
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-feelpp-hpcops.pdf}
    \caption{CI/CD HPCOps for Feel++}
    \label{fig:feelpp-hpcops}
\end{figure}

@@

\Cref{fig:kub-devops} shows that the CI/CD standard DevOps framework for KUB uses similar steps.

\Cref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot on large-scale cases. It extends Feel++ HPC ops with additional steps to handle our complex pre- and post-processing steps.

@@

Finally, we display some results of our benchmarking activities~\cite{hidalgo2_d31_2024} for the KUB application regarding HPC performance.
Running these experiments regularly is essential for maintaining the program's efficiency when developing the application and after machine updates.
Hence, we have used the KUB application in the Strasbourg city center, with a square area of $4 \mathrm{km}^2$ (approximately 17K buildings).
The scalability results were realized on EuroHPC JU systems obtained with our HPCOps pipeline; see \cref{fig:kub-hpcops}.
\Cref{fig:scalability} depicts the speedup achieved on Discoverer, Karolina, and MeluXina.
They present results for the total execution (end-to-end) of the KUB application and the simulation component.

@@

To better understand what causes this degradation, we measure the computing times of the different stages of the pipeline and present the execution breakdown in \cref{fig:execution-breakdown}. 
\cref{fig:execution-breakdown} reports the portion of the total execution taken by:
\begin{itemize}
\item Pre-processing (Pre-proc): The time elapsed in initialization before entering the time loop of the simulation
\item Simulation (Simulation): The cumulative time spent calculating the new solution at each time step
\item Post-processing (Post-proc): The cumulative time spent exporting results, i.e., generating files containing the output of the UB model.
\end{itemize}
